Note on: Out-of-Sample Error for Laplacian Eigenmaps

### 2021-02-17 notes/weekly_notes/12.24.20.NotesForWeek.tex
Updated the document regarding extension of Laplacian estimators.

The estimate we will consider is a kernel smoother passed over $\wh{\theta}$,
\begin{equation*}
\wh{f}(x) := T_{\varepsilon,n}\wh{\theta}_{1:n}(x).
\end{equation*}
In order to relate the out-of-sample error $\|\wh{f} - f^{\ast}\|_P$ to the in-sample error $\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n$, we will assume the following.
\begin{enumerate}[label=(A\arabic*)]
	\item
	\label{asmp:kernel}
	The kernel function $\eta$ is supported on a subset of $[0,1]$, with $\eta(1/2) > 0$. Additionally, $\eta$ is \textcolor{red}{Lipschitz} on its support.
	\item 
	\label{asmp:domain} There exists $\alpha > 0$ such that for every $x \in \mc{X}$, $d_{\nu}(x) \geq \alpha \cdot \varepsilon^d$.
	\item 
	\label{asmp:density}The distribution $P$ admits a density $p$ with respect to Lebesgue measure. The density $p \in C^1(\mc{X})$, and is bounded away from $0$ and $\infty$ for all $x \in \mc{X}$,
	\begin{equation*}
	0 < p_{\min} \leq p(x) < p_{\max} < \infty.
	\end{equation*}
\end{enumerate}
Under Assumption~\ref{asmp:kernel}, we automatically have that $d_\nu(x) = \varepsilon^d$ for all $x \in \mc{X}_{\varepsilon}$. Assumption~\ref{asmp:domain} is thus a condition on the boundary $\partial \Omega$, and is implied for all sufficiently small $\varepsilon$ if the boundary is Lipschitz. 
\begin{lemma}
	\label{lem:kernel_smoothing_laplacian_eigenmaps}
	Suppose $f^{\ast} \in H^1(\mc{X})$ and $p \in C^1(\mc{X})$. Then with probability at least $1 - \delta - C\varepsilon^d\exp\{-Cn\varepsilon^d\}$, it holds that
	\begin{equation*}
	\|\wh{f} - f^{\ast}\|_P^2 \leq C\biggl(\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n^2 + \frac{1}{\delta} \cdot \frac{\varepsilon^2}{n\varepsilon^d} |f|_{H^1(\mc{X})}^2 + \frac{1}{\delta}\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2\biggr)
	\end{equation*}
\end{lemma}
Notice that the variance term in the above is smaller than the typical variance term for kernel smoothing of noisy data (on the order of $1/(n\varepsilon^d)$) by a factor of $\varepsilon^2$. The bias term, on the other hand, is standard, and in particular the following estimate of the bias can be obtained. 
\begin{lemma}
	Suppose $f^{\ast} \in H_0^{s}(\Omega)$, $p \in C^{\beta}(\Omega)$ for $\beta = s - 1$, and that $\eta$ is an order-$s$ kernel. Then
	\begin{equation*}
	\|T_{P,\varepsilon}f^{\ast} - f^{\ast}\|_P^2 \leq C \varepsilon^{2s}.
	\end{equation*}
\end{lemma}

>>>>

The estimate we will consider is a kernel smoother passed over $\wh{\theta}$,
\begin{equation}
\label{eqn:kernel_smoother_laplacian_eigenmaps}
\wh{f}(x) := T_{\varepsilon,n}\wh{\theta}_{1:n}(x).
\end{equation}
In order to relate the out-of-sample error $\|\wh{f} - f^{\ast}\|_P$ to the in-sample error $\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n$, we will assume the following.
\begin{enumerate}[label=(A\arabic*)]
	\item
	\label{asmp:kernel}
	The kernel function $\eta$ is supported on a subset of $[0,1]$, with $\eta(1/2) > 0$. Additionally, $\eta$ is \textcolor{red}{Lipschitz} on its support.
	\item 
	\label{asmp:domain} There exists $\alpha > 0$ such that for every $x \in \mc{X}$, $d_{\nu}(x) \geq \alpha \cdot \varepsilon^d$.
	\item 
	\label{asmp:density}The distribution $P$ admits a density $p$ with respect to Lebesgue measure. The density $p \in C^1(\mc{X})$, and is bounded away from $0$ and $\infty$ for all $x \in \mc{X}$,
	\begin{equation*}
	0 < p_{\min} \leq p(x) < p_{\max} < \infty.
	\end{equation*}
\end{enumerate}
Under Assumption~\ref{asmp:kernel}, we automatically have that $d_\nu(x) = \varepsilon^d$ for all $x \in \mc{X}_{\varepsilon}$. Assumption~\ref{asmp:domain} is thus a condition on the boundary $\partial \Omega$, and is implied for all sufficiently small $\varepsilon$ if the boundary is Lipschitz. 
\begin{lemma}
	\label{lem:kernel_smoothing_laplacian_eigenmaps}
	Suppose $f^{\ast} \in H^1(\mc{X})$ and $p \in C^1(\mc{X})$. Then with probability at least $1 - \delta - C\varepsilon^d\exp\{-Cn\varepsilon^d\}$, it holds that
	\begin{equation*}
	\|\wh{f} - f^{\ast}\|_P^2 \leq C\biggl(\|\wh{\theta}_{1:n} - f^{\ast}_{1:n}\|_n^2 + \frac{1}{\delta} \cdot \frac{\varepsilon^2}{n\varepsilon^d} |f|_{H^1(\mc{X})}^2 + \frac{1}{\delta}\|T_{\varepsilon,P}f^{\ast} - f^{\ast}\|_P^2\biggr)
	\end{equation*}
\end{lemma}
Notice that the variance term in the above is smaller than the typical variance term for kernel smoothing of noisy data (on the order of $1/(n\varepsilon^d)$) by a factor of $\varepsilon^2$. The bias term, on the other hand, is standard, and in particular the following estimate of the bias can be obtained. 
\begin{lemma}
	Suppose $f^{\ast} \in H_0^{s}(\Omega)$, $p \in C^{\beta}(\Omega)$ for $\beta = s - 1$, and that $\eta$ is an order-$s$ kernel. Then
	\begin{equation*}
	\|T_{P,\varepsilon}f^{\ast} - f^{\ast}\|_P^2 \leq C \varepsilon^{2s}.
	\end{equation*}
\end{lemma}
